---
title: "September 18"
date: "Last compiled on `r format(Sys.time(), '%d %B, %Y, %H : %M : %S')`"
output:
  html_document:
    df_print: paged
---

### When you are finished *knit*/*render* your R Studio document or turn in a written copy on paper but show your work in order..

#### You may compute your answers using a calculator, pen and paper, or R. 

#### For the next problems use these as your data:

**-1,-5,7,21,15,-3,10,11,14,8**

1. What is the sum of these?
2. What is the mean?
3. What is the variance?
4. What is the standard deviation?

```{r}
p1 <- c(-1,-5,7,21,15,-3,10,11,14,8)
sum(p1)
mean(p1)
var(p1)
sd(p1)

```

#### For the next problems use these as your data:

**1,2,2,3,3,3,4,4,4,4,4,5,5,5,6,6,7**

5. What is the mode of these?
6. What is the median?
7. What is the sum of these?
8. How many observations are there?
9. What is the mean?

```{r}

p2 <- c(1,2,2,3,3,3,4,4,4,4,4,5,5,5,6,6,7)
median(p2)
sum(p2)
length(p2)
mean(p2)

```

#### For the next problem use these as your data:

**5,10,15,20**

10. What is the median of the data?

```{r}

p3 <- c(5,10,15,20)
median(p3)

```

11. What is the name of the President of the University of Houston? (first, last, spelling does not count)