---
title: |
    | Problem Set 4
    | Statistical Tests
    | POLS3316: Statistics for Political Scientists
    | Due November 15, 2023 at 11:59pm
author: "Charlie Tran"
format: 
        html:
                self-contained: true
---


## Use this work file if working in R

It is recommended to use this .qmd file to complete your work if working in R. Simply edit your name in the second line. 

## General instructions

`#` indicates that the line is a comment and does not need to be edited.

The significance level for all tests is .05 unless otherwise specified.

Type only code in the code chunks. Do not type answers as comments in the code chunks.

Type answers in the text chunks.

You can get help with the functions using the ? command in the Console (lower left)

To complete Bonus Problem 7, you will need to install a package and load a library. Instructions are given. You will not be able to get help for the z.test using the ? until the package is installed.

## Problem 1: Chi-square

Complete a Chi-square test of independence on the following data using the R function `chisq.test()`.

| | 1 | 2 | 
| --- | --- | --- |
| A | 10 | 20 |
| B | 15 | 25 |

```{r}
# Your code here
a <- c(10,15)
b <- c(20,25)
ab <- cbind(a,b)
ab

chisq.test(ab, correct = FALSE)

```
X-squared: 0.12963

p-value: 0.7188

Is the test significant? Why or why not?
Since the p-value of 0.914 is greater the significant level of 0.05, the test is not significant.

## Problem 2: Chi-square

Complete a Chi-square test of independence on the following data using the R function `chisq.test()`.

| | 1 | 2 | 3 | 4 | 
| --- | --- | --- | --- | --- |
| A | 10 | 20 | 30 | 40 |
| B | 15 | 25 | 35 | 45 |
| C | 20 | 30 | 40 | 50 |

```{r}
one <- c(10,15,20)
two <- c(20,25,30)
three <- c(30,35,40)
four <- c(40,45,50)

one2four <- cbind(one,two,three,four)
one2four

chisq.test(one2four, correct=FALSE)

```

Chi-squared: 1.2408

p-value: 0.9748

Is the test significant? Why or why not?
Since the p-value of 0.9748 is greater than the significant level of 0.05, the test is not significant.             

## Problem 3: t-test

Complete a paired sample t-test on the following data using the R function `t.test()`. Complete a two-tailed test.

| | Before | After |            
| --- | --- | --- |
| A | 10 | 20 |
| B | 24 | 25 |
| C | 18 | 30 |
| D | 25 | 35 |
| E | 41 | 40 |
| F | 35 | 45 |



```{r}

before <- c(10,24,18,25,41,35)
after <- c(20,25,30,25,40,45)

t.test(before,after,paired = TRUE, alternative = "two.sided")

```



t-score: -2.2061

p-value: 0.07849

Is the test significant? Why or why not?
Since the p-value of 0.07849 is greater than the significance level of 0.05, we can conclude that the test is not significant and the true mean difference is not equal to zero. 

## Problem 5: t-test

Complete a one-sample t-test on the following data using the R function `t.test()`. Complete a two-tailed test.

| | 1 | 2 | 3 | 4 | 5 | 6 | 7 | 8 | 9 | 10 |
| --- | --- | --- | --- | --- | --- | --- | --- | --- | --- | --- |
| A | 10 | 20 | 30 | 40 | 50 | 60 | 70 | 80 | 90 | 100 |

```{r}

one_samp_t <- cbind(10,20,23,40,50,60,70,80,90,100)
one_samp_t

t.test(one_samp_t)

```

t-score: 5.5407

p-value: 0.0003607                

Is the test significant? Why or why not?
The test is significant because the p-value of 0.0003607 is less than 0.05

## Problem 6: Bonus

Complete a one-way ANOVA on the following data using the R function `aov()`. Complete a two-tailed test.

| | 1 | 2 | 3 | 4 |
| --- | --- | --- | --- | --- |
| A | 10 | 20 | 30 | 40 |
| B | 15 | 25 | 35 | 45 |
| C | 20 | 30 | 40 | 50 |

```{r}
# Create a vector for each group with its corresponding values
group <- c('a','a','a','a','b','b','b','b','c','c','c','c')

value <- c(10,20,30,40,15,25,35,45,20,30,40,50)

problem6 <- data.frame(group, value)

problem6_aov <- aov(value ~ group, data = problem6) 
summary.aov(problem6_aov)
```

Is the test significant? Why or why not?
Since the p-value of 0.569 is greater than the significant level of 0.05, the test is not significant.   

## Problem 7: Bonus

Complete a z-test on the following data using the R function `z.test()`. Complete a two-tailed test.

| | obs 1 | obs 2 | obs 3 | obs 4 | obs 5 | obs 6                
| --- | --- | --- | --- | --- | --- | --- |
| A | 10 | 20 | 30 | 40 | 50 | 60 |
| B | 15 | 25 | 35 | 45 | 55 | 65 |              


```{r}
# To run a z.test, you will need to install the BSDA package and load the library

# To do this, remove the # from the following two lines of code and run them

#install.packages("BSDA")
library(BSDA)

obs_a <- c(10,20,30,40,50,60)
obs_b <- c(15,25,35,45,55,65)
sd(obs_a)
sd(obs_b)

prob7 <- cbind(obs_a,obs_b)

z.test(obs_a, obs_b, alternative = "two.sided", sigma.x = sd(obs_a), sigma.y = sd(obs_b))

```
z-score here: -0.46291

p-value here: 0.6434

Is the test significant? Why or why not?
Since the p-value of 0.6434 is greater than the significant level of 0.05, the test is not significant.   

